%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.35in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemCustom}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\hypersetup{colorlinks=true,linkcolor=blue, linktocpage}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Morphy Kuffour}} & \href{https://www.linkedin.com/in/morphy-kuffour/}{LinkedIn}  \href{https://github.com/morphykuffour}{GitHub}\\
  \href{mailto:morpkuff@protonmail.com}{morpkuff@protonmail.com}  & \href{https://morphykuffour.github.io/}{Personal Blog}\\
   860-573-6681\\
\end{tabular*}
%-----------PROFESSIONAL SUMMARY-----------------
\\
\vspace{5pt}
%Motivated and growth-oriented professional seeking to expand my technical expertise, develop versatile skills, and build meaningful %industry relationships—while delivering impactful solutions and contributing to organizational success.

%Versatile and growth-driven technology professional with a strong foundation in software development, infrastructure, and product management. Experienced in delivering solutions across cross-functional teams and driving operational improvements through automation and innovation. Committed to continuous learning, building impactful systems, and growing into a leadership role within the tech industry.

Versatile and growth-oriented technology professional with experience in software development, infrastructure, and Product management. Focused on building impactful solutions and evolving toward technical leadership.


%-----------EDUCATION-----------------
\section{~~Education}
\vspace{5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Connecticut}{Storrs, CT, USA}
      {B.S.E, Computer Science and Engineering}{Aug 2019 - May 2023}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Relevant Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Machine Learning, Networking, Databases}}}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Programs \& Clubs:}
  UConn Honors Program, UConn Upsilon Pi Epsilon, Louis Stokes Alliance for Minority Participation (LSAMP), National Society for Black Engineers (NSBE), UConn Cybersecurity Club, UConn Honors Society}}}
    \resumeSubHeadingListEnd
	    
\vspace{1pt}
\section{Skills Summary}
\vspace{1pt}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Lua, Nix, Python, Bash, awk, C, Powershell}
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Neovim, Emacs, Docker, Vagrant, Git, SQL, Excel (data analysis)}
	\resumeSubItem{Platforms}{~~~~~~~Linux, NixOS, OSX, Web, Windows XP/7/10/11, Windows Server 2016}
	\resumeSubItem{Certifications}{~~CompTIA Security+ (In Progress), RHCSA (In Progress), RHCE (In Progress)}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Effective Verbal and Written Communication Skills, Time Management}
\resumeSubHeadingListEnd

\vspace{1pt}
\section{Relevant Experience}
\vspace{5pt}
  \resumeSubHeadingListStart
    \resumeSubheading{Raytheon Technologies}{Remote}
    {Digital Leadership Development Program Associate}{May 2023 - Present}
    \resumeItemListStart
    \resumeItemCustom{}{\textbf{Rotation 1}: Software Developer at Corporate Raytheon Technologies}
    \\
    \vspace{4pt}
    Developed a PowerShell solution to update Managed Metadata fields in SharePoint, integrating Term Store taxonomy for consistent document classification. Streamlined metadata updates as part of a compliance automation initiative, reducing manual effort and ensuring data governance.
    
    \resumeItemCustom{}{\textbf{Rotation 2}: Technical Product Manager at Pratt \& Whitney}
    \\
    \vspace{4pt}
    Worked with the Engineering Applications team to modernize internal tooling by leading the migration from Lotus Notes to Mendix. Streamlined workflows and improved application lifecycle management by leveraging Jira for project tracking and coordination. Additionally, automated a data reporting pipeline to enhance efficiency and reduce manual workload. Collaborated with cross-functional teams to ensure a smooth transition and drive process improvements in engineering operations.

    \resumeItemCustom{}{\textbf{Rotation 3}: Cloud Data Engineer at Pratt \& Whitney}
    \\
    \vspace{4pt}
    Working with the Connected Factory team to develop and deploy AI-driven solutions at an enterprise scale. Focused on Machine Learning Operations (MLOps) to streamline model deployment and monitoring. Building optimized cloud-based data pipelines using Python, Azure Functions, and Azure Data Factory to support AI initiatives. Collaborating with cross-functional teams to enhance data workflows and improve operational efficiency in manufacturing environments.
    \resumeItemListEnd
    
\vspace{2pt}
    \resumeSubheading{Raytheon Technologies}{Remote}
    {Digital Leadership Development Program Intern}{Aug 2021 - May 2023}
    \resumeItemListStart
    \resumeItemCustom{}{Worked with Raytheon Technologies Corporate Identity Access Solutions team to facilitate Multi-Factor Authentication (MFA) solutions for over 30,000 employees.}
    \resumeItemListEnd
    
\vspace{2pt}
    \resumeSubheading{UConn Research Assistant}{Hybrid - Storrs, CT}
    {Undergraduate Research Assistant}{Aug 2021 - May 2023}
    \resumeItemListStart
    \resumeItemCustom{}{Worked with Prof. Clay Tabor on porting Community Earth System Model (CESM) to the UConn high performance computing system.}
    \resumeItemListEnd
    
\vspace{2pt}
    \resumeSubheading{UConn Teaching Assistant}{Storrs, CT}
    {Undergraduate Teaching Assistant for CSE 3140}{Jan. 2022 - Dec 2022}
    \resumeItemListStart
    \resumeItemCustom{}{Assist students in CSE 3140, a cybersecurity lab course, and provide office hours to answer student questions regarding coursework. Skills: Shell Scripting, Linux Configuration, Debugging, Cybersecurity}
    \resumeItemListEnd
    
\vspace{2pt}
    \resumeSubheading{UConn Teaching Assistant}{Storrs, CT}
    {Undergraduate Teaching Assistant for CSE 1010}{Aug. 2021 - Jan 2022}
    \resumeItemListStart
    \resumeItemCustom{}{Assist students in CSE 1010, an introductory computer science course taught in Python and MATLAB, and provide office hours to answer student questions regarding course work.}
    \resumeItemListEnd
    
\vspace{2pt}
    \resumeSubheading
		{UConn Information Technology Services}{Storrs, CT}
		{UITS Network Assistant}{ Jan. 2021 - Jun. 2021}
		\resumeItemListStart
        \resumeItemCustom{}{Duties included troubleshooting network hardware related problems, remotely configuring routers and access points, conducting wireless surveys, and working with Cisco Prime Infrastructure software to manage subnets on the UConn Campus.}
		\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\section{Achievements}
    \resumeSubheading
            {1st Place UConn Senior Design Project}
		{University of Connecticut}{May 2023}
            {Project: \href{https://seniordesignday.engr.uconn.edu/seniorprojectpt/senior-design-2023-computer-science-and-engineering-team-05/}{HuskyFit Mobile Application}}
            \resumeItemListStart
        \resumeItemCustom{}{Part of a team that designed a Health and Fitness Mobile Application}
        \resumeItemCustom{}{Utilized React framework, AWS technologies, and other software development tools to simplify the development process }
        \resumeItemCustom{}{Presented the project to industry experts, securing 1st Place in the design competition.}
        \resumeItemCustom{}{Competed against 39 Engineering teams to achieve this recognition.}
		\resumeItemListEnd





%-----------PROJECTS-----------------
\vspace{5pt}
\section{Projects}
\vspace{5pt}
\resumeSubHeadingListStart
\resumeSubItem{\href{https://github.com/morphykuffour/nix.git}{Cross Platform Nix Configuration}}{System-wide configuration for Linux, Windows Subsystem for Linux(WSL), and Mac OS X.  Tech: Nix, NixOS, Bash, OSX, WSL}
\vspace{2pt}
\resumeSubItem{\href{https://github.com/morphykuffour/lookup.nvim.git}{lookup.nvim}}{Lookup up the definition of a word under the cursor in neovim, a terminal text editor. Tech: Neovim, Lua, Rest APIs}
\vspace{2pt}
\resumeSubItem{\href{https://github.com/morphykuffour/rawtalk.git}{rawtalk}}{ (Work in progress) A userspace tool that leverages hidapi library to communicate with a qmk enabled keyboard to perform layout switching and other useful tasks. Tech: Rust, nix}
\vspace{2pt}
\resumeSubItem{\href{https://morphykuffour.github.io/keyboards,/ergonomics,/qmk/2021/12/29/Dactyl-Manuform.html}{Dactyl Manuform 5x6 Keyboard Build}}{Built a custom Dactyl Manuform Keyboard, a parameterized, split-hand, concave, columnar, ergonomic keyboard. Skills: Wiring, PCB Soldering, Hardware debugging. Tech: C}
\vspace{2pt}
\resumeSubHeadingListEnd


%-- \vspace{-5pt}
 
\vspace{5pt}
\section{Interests}
\vspace{5pt}
Playing soccer, basketball, and working out. Building and modifying custom mechanical keyboards. Writing nix to create a reproducible, custom, cross-platform system for NixOS(Linux), MacOSX(Darwin) and Windows (WSL). Improving my productivity, learning new programming techniques and languages. I also enjoy writing about the technology I use on my blog: \href{https://morphykuffour.github.io/}{morphykuffour.github.io}. \\
\end{document}
