% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\usepackage[hidelinks]{hyperref}
%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

%-----------------------------------------------------------
%\usepackage{fullpage}
\usepackage{shading}
%\textheight=9.0in
\pagestyle{empty}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item[] #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \parashade[.9]{sharpcorners}{\textbf{#1 \vphantom{p\^{E}}}}}}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{tabular*}{6.8in}{l@{\extracolsep{\fill}}r}
\textbf{\Large Morphy Kuffour}  & 860 573 6681\\
100 Shoddy Mill Road &  morphy.kuffour@uconn.edu \\
Bolton, CT 06043 & \href{https://www.linkedin.com/in/morphy-kuffour-4279bb174/}{LinkedIn}\\
\end{tabular*}
\\

\resheading{Education}
	\ressubheading{University of Connecticut}{Storrs, CT}{B.S.E., Computer Science and Engineering (GPA: 3.78)}{Aug. 2019 - Present}
	\ressubheading{}{}{B.S, Applied Mathematics (GPA: 3.78)}{Aug. 2019 - Present}
	\begin{itemize}
		\resitem{Relevant courses: Object Oriented Programming \& Design, Algorithms \& Complexity, Principles of Programming Languages, Systems Programming, Discrete Systems, Digital Logic Design, Computer Architecture 
		}
		\resitem{Programs \& Clubs: UConn Honors Program, UConn Upsilon Pi Epsilon, Louis Stokes Alliance for Minority Participation (LSAMP), National Society for Black Engineers (NSBE), UConn Cybersecurity Club, UConn Honors Society}
	\end{itemize}

\resheading{Relevant Employment Experience}
\begin{itemize}
\item
	\ressubheading{Raytheon Technologies}{Remote}{Digital Leadership Development Program
	 Intern}{Aug 2021 - Present}
	\begin{itemize}
		\resitem{Working with Raytheon Technologies Corporate Identity Access Solutions team to facilitate Multi-Factor Authentication (MFA) solutions for over 30,000 employees.}
	\end{itemize}

\item 
\ressubheading{Teaching Assistant}{Storrs, CT}{Undergraduate Teaching Assistant for CSE 1010}{Aug. 2021 - Present}
	\begin{itemize}
		\resitem{Assist students in CSE 1010, an introductory computer science course taught in Python and MATLAB, and provide office hours to answer student questions regarding course work.}
	\end{itemize}

\item
\ressubheading{Connecticut Carpentry Corporation}{Storrs, CT}{Construction Worker}{May. 2021 - Jul. 2021}
\begin{itemize}
	\resitem{Contributing member of small crew responsible for site-preparation and other various tasks.}
\end{itemize}

\item
	\ressubheading{UConn Information Technology Services}{Storrs, CT}{UITS Network Assistant}{Jan. 2021 - Jun. 2021}
	\begin{itemize}
		\resitem{Duties include troubleshooting network hardware related problems, remotely configuring routers and access points, conducting wireless surveys, and working with Cisco Prime Infrastructure software to manage subnets on the UConn Campus.}
	\end{itemize}


\item
	\ressubheading{UConn Office of Residential Life}{Storrs, CT}{Service Desk Assistant}{Aug 2020 - Jan. 2021}
	\begin{itemize}
		\resitem{Duties include using proprietary software to check students in and out of housing assignments, distributing, and
			collecting room keys, and providing customer service to UConn students and the public regarding housing procedures.}
	\end{itemize}
\item
\ressubheading{Charlestown Mini-Super}{Charlestown, RI}{Supermarket Employee}{Jun. 2020 - Aug. 2020}
\item
\ressubheading{Kingston Pizza}{Charlestown, RI}{Restaurant Employee}{Jun. 2020 - Aug. 2020}
\end{itemize}

\resheading{Technical Skills}
\begin{description}
\item[Languages:]
C, C++, Python, RISC-V, \LaTeX, and lua
\item[Operating Systems:] Linux (Debian, Arch Linux), MacOS X, Windows 7/10, Windows 2016 Server
\item[Applications:] bash, tmux, vim, powershell, qira, gdb, git, bash, pandoc, Windows Subsystem for Linux(WSL2),  LibreOffice, MS Office, Enterprise Splunk\\
\item[Miscellaneous:] fundamental understanding of information security and computer networks, software configuration management, effective verbal and written communication skills within a team environment, excellent troubleshooting and debugging skills, productivity, strong problem solving skills
\end{description}

%\iffalse
\resheading{Interests}
Playing soccer, basketball, and fitness.
Building and modding keyboards, customizing my Linux OS, improving my productivity, learning new programming techniques and languages.
%\fi


\end{document}
